Stat 534 Project: \\ Extrapolation from Poisson Process Intensity Surface Models

### 2017-03-22 project/paper.rnw
Just need to make plots and wrap up for the presentation.

<<polyfit1, warning = FALSE, fig.width = 6, fig.height = 8, fig.pos = 'p', fig.cap = ''>>=
# Create a quadrature scheme manually to ensure there are dummy points on
# each transect.
# TODO: Figure out weights.
ex_Q <- quad(data = ex_ppp,
             dummy = as.ppp(rbind(
               data.frame(vertices(Window(ex_ppp))),
               do.call(rbind, lapply(unique(ex_path$x), function(x){
                 return(data.frame(
                   x = x, y = seq(min(ex_path$y), max(ex_path$y),
                                  length.out = 128)
                 ))}))), W = Window(ex_ppp)))

@@

# Multiply predictions by 43560 to convert from anomalies per square foot
# to anomalies per acre.
plot(43560 * predict(ex_fit2, window = site_window), main = '2nd Degree')
plot(43560 * predict(ex_fit3, window = site_window), main = '3rd Degree')
plot(43560 * predict(ex_fit4, window = site_window), main = '4th Degree')
plot(43560 * predict(ex_fit5, window = site_window), main = '5th Degree')
plot(43560 * predict(ex_fit6, window = site_window), main = '6th Degree')
plot(43560 * predict(ex_fit7, window = site_window), main = '7th Degree')
plot(43560 * predict(ex_fit8, window = site_window), main = '8th Degree')
plot(43560 * predict(ex_fit9, window = site_window), main = '9th Degree')
plot(43560 * predict(ex_fit10, window = site_window), main = '10th Degree')
plot(43560 * predict(ex_fit11, window = site_window), main = '11th Degree')
plot(43560 * predict(ex_fit12, window = site_window), main = '12th Degree')
plot(43560 * density(ex_ppp_full) * area(ex_ppp_full) / ex_ppp_full$n,
     main = 'Kernel Density')
@

>>>>

<<polyfit1, cache = TRUE, warning = FALSE, fig.width = 6, fig.height = 8, fig.pos = 'p', fig.cap = ''>>=
# Create a quadrature scheme manually to ensure there are dummy points on
# each transect.
# TODO: Figure out weights.
ex_Q <- quad(data = ex_ppp,
             dummy = as.ppp(rbind(
               data.frame(vertices(Window(ex_ppp))),
               do.call(rbind, lapply(unique(ex_path$x), function(x){
                 return(data.frame(
                   x = x, y = seq(min(ex_path$y), max(ex_path$y),
                                  length.out = 128)
                 ))}))), W = Window(ex_ppp)))

@@

# Get predictions and SEs.
ex_p2 <- predict(ex_fit2, window = site_window, se = TRUE)
ex_p3 <- predict(ex_fit3, window = site_window, se = TRUE)
ex_p4 <- predict(ex_fit4, window = site_window, se = TRUE)
ex_p5 <- predict(ex_fit5, window = site_window, se = TRUE)
ex_p6 <- predict(ex_fit6, window = site_window, se = TRUE)
ex_p7 <- predict(ex_fit7, window = site_window, se = TRUE)
ex_p8 <- predict(ex_fit8, window = site_window, se = TRUE)
ex_p9 <- predict(ex_fit9, window = site_window, se = TRUE)
ex_p10 <- predict(ex_fit10, window = site_window)
ex_p11 <- predict(ex_fit11, window = site_window)
ex_p12 <- predict(ex_fit12, window = site_window)

# Multiply predictions by 43560 to convert from anomalies per square foot
# to anomalies per acre.
plot(43560 * ex_p2$estimate, main = '2nd Degree')
plot(43560 * ex_p3$estimate, main = '3rd Degree')
plot(43560 * ex_p4$estimate, main = '4th Degree')
plot(43560 * ex_p5$estimate, main = '5th Degree')
plot(43560 * ex_p6$estimate, main = '6th Degree')
plot(43560 * ex_p7$estimate, main = '7th Degree')
plot(43560 * ex_p8$estimate, main = '8th Degree')
plot(43560 * ex_p9$estimate, main = '9th Degree')
plot(43560 * ex_p10, main = '10th Degree')
plot(43560 * ex_p11, main = '11th Degree')
plot(43560 * ex_p12, main = '12th Degree')
plot(43560 * density(ex_ppp_full) * area(ex_ppp_full) / ex_ppp_full$n,
     main = 'Kernel Density')
@

<<polyse1, fig.width = 6, fig.height = 8, fig.pos = 'p', fig.cap = ''>>=
par(mfrow = c(4, 3), mar = c(1, 0, 2, 3), las = 2, cex = 1)
plot(log(43560 * ex_p2$se), main = '2nd Degree\nlog(SE)', zlim = c(6.5, 10.5))
plot(log(43560 * ex_p3$se), main = '3rd Degree\nlog(SE)', zlim = c(6.5, 10.5))
plot(log(43560 * ex_p4$se), main = '4th Degree\nlog(SE)', zlim = c(6.5, 10.5))
plot(ex_p2$se / ex_p2$estimate, main = '2nd Degree\nRSE', zlim = c(0, 2))
plot(ex_p3$se / ex_p3$estimate, main = '3rd Degree\nRSE', zlim = c(0, 2))
plot(ex_p4$se / ex_p4$estimate, main = '4th Degree\nRSE', zlim = c(0, 2))

plot(log(43560 * ex_p6$se), main = '6th Degree\nlog(SE)', zlim = c(6.5, 10.5))
plot(log(43560 * ex_p8$se), main = '8th Degree\nlog(SE)', zlim = c(6.5, 10.5))
plot(log(43560 * ex_p9$se), main = '9th Degree\nlog(SE)', zlim = c(6.5, 10.5))
plot(ex_p6$se / ex_p6$estimate, main = '6th Degree\nRSE', zlim = c(0, 2))
plot(ex_p8$se / ex_p8$estimate, main = '8th Degree\nRSE', zlim = c(0, 2))
plot(ex_p9$se / ex_p9$estimate, main = '9th Degree\nRSE', zlim = c(0, 2))
@

### 2017-03-22 project/pres.rnw
Just need to make plots and wrap up for the presentation.

<<uxoexampledata>>=
# Define the window for the UXO site.
site_window <- owin(poly = cbind(x = c(1564294, 1564495, 1556870, 1557126),
                                 y = c(535421, 541130, 541085, 535576)),
                    unitname = c('foot', 'feet'))
@

@@

>>>>

<<uxoexampledata>>=
# Define the window for the UXO site.
site_window <- owin(poly = cbind(x = c(1564294, 1564495, 1556870, 1557126),
                                 y = c(535421, 541130, 541085, 535576)),
                    unitname = c('foot', 'feet'))
ex_anom <- read.csv('easy_sample_tTA2_p200_bg100_fg200_rep2000.anomaly')
ex_path <- read.csv('easy_sample_tTA2_p200_bg100_fg200_rep2000.cog')
ex_win <- intersect.owin(site_window,
  do.call(union.owin, lapply(unique(ex_path$x), function(x){
    return(owin(c(x - 3, x + 3), c(535421, 541130),
           unitname = c('foot', 'feet')))
  })))
ex_ppp <- ppp(ex_anom$x, ex_anom$y, window = ex_win)
ex_ppp_full <- ppp(ex_anom$x, ex_anom$y, window = site_window)
@

@@

\begin{frame}
\frametitle{Observed Events}

\item Metal detectors record anomalies in six foot wide strips along parallel
transects with 396 feet between centerlines

\item Observed \Sexpr{sprintf('%.1f', area(ex_win) / 43560)} acres,
\Sexpr{sprintf('%.1f\\%%', 100 * area(ex_win) / area(site_window))}
of the site

<<sim2000obs>>=
par(mar = c(0, 0, 1, 0))
plot(ex_ppp, main = 'Observed Geomagnetic Anomalies', pch = '.', border = NA)
plot(site_window, add = TRUE)
@
\end{frame}

\begin{frame}
\frametitle{Models}

\item Polynomial models
\(\displaystyle\log(\lambda(x,y))
= \sum_{i=0}^{p}\sum_{j=0}^{p-i}\beta_{ij}x^{i}y^{j}\)
for \(p = 2, 3, \dots, 12\)

<<dummy, warning = FALSE>>=
ex_fit1 <- ppm(ex_ppp_full ~ x + y)
ex_Q <- quad(data = ex_ppp,
             dummy = as.ppp(rbind(
               data.frame(vertices(Window(ex_ppp))),
               do.call(rbind, lapply(unique(ex_path$x), function(x){
                 return(data.frame(
                   x = x, y = seq(min(ex_path$y), max(ex_path$y),
                                  length.out = 128)
                 ))}))), W = Window(ex_ppp)))

par(mfrow = c(1, 2), mar = c(0, 0, 1, 0), cex = 1)
plot(ex_fit1$Q$dummy, pch = '.', border = NA,
     main = 'Default Dummy Points')
plot(site_window, add = TRUE)
plot(ex_Q$dummy, pch = '.', border = NA,
     main = 'Manual Dummy Points')
plot(site_window, add = TRUE)
@

\begin{frame}
\frametitle{Problems with Implementation}

\item Needed to rescale coordinates

\item For \(p \geq 10\), \texttt{pmm} cannot compute SEs because the
``Fisher information matrix is singular''

\item The \texttt{plot} method gives an error about infinite values

\item When the window isn't specified, the \texttt{predict} method's default
grid misses all but two transects

\item The predict method does not work with spline smoothers

\item The magnitudes of the predictions are much to large
